Meeting Agenda with Domain Experts

### 2021-01-04 StateOfPractice/Methodology/Meeting Agenda with Domain Experts.tex
Clarified 3 times of interaction with the domain experts

\subsection{About this Meeting}
Presenter: \ad{TBD}

@@

\section{Qualities \& Measurements}

>>>>

\subsection{3 Steps for Domain Experts}
The domain experts are expected to participate in the following 3 steps:
\begin{itemize}
\item Step 1 - introductory meeting. This is our current meeting, which will
lasts for about one hour.
\item Step 2 - measuring. Usability experiments, modifiability experiments, and
developer interviews are included in this step. More details will be discussed
later in Section \ref{qualities_Measurements}.
\item Step 3 - concluding meeting. Our second and the last meeting, aiming to be
one hour in duration. Results of ranking will be discussed.
\end{itemize}

\subsection{About this Meeting (Introductory Meeting)}
Presenter: \ad{TBD}

@@

\section{Qualities \& Measurements}
\label{qualities_Measurements}
